Formulating Regional Typologies

### 2023-11-01 regional_typologies.qmd
updated tables

### List of potential features

### Collected data

| No  | Data                                                    | Source                                                  | Unit           |
|------|---------------------------------|------------------------|------------------|

@@

| 14  | Deforestation area size                                 | Land cover map 2020, MoEF                               | kmē            |
| 15  | Arable land (%)                                         | Land cover map 2020, MoEF                               | %/Sub district |
| 16  | Erosion                                                 | RUSLE                                                   | t ha?1 yr?1    |

@@

| 20  | Total families based on electricity users and non-users | Potensi desa BPS 2019                                   | number         |
| 21  | Electrification ratio                                   | Potensi desa BPS 2019                                   | number         |
| 22  | High school ratio                                       | Potensi desa BPS 2019                                   | number         |
| 23  | University ratio                                        | Potensi desa BPS 2019                                   | number         |
| 24  | Hospital ratio                                          | Potensi desa BPS 2019                                   | number         |
| 25  | Health facility ratio                                   | Potensi desa BPS 2019                                   | number         |
| 26  | Market ratio                                            | Potensi desa BPS 2019                                   | number         |
| 27  | Minimarket ratio                                        | Potensi desa BPS 2019                                   | number         |

@@

| 40  | Reservoir ratio                                         | Potensi desa BPS 2019                                   | number         |
| 41  | Ratio of village markets                                | Potensi desa BPS 2019                                   | number         |
| 42  | Number of people suffering from malnutrition 2018       | Potensi desa BPS 2019                                   | number         |
| 43  | Ratio of people suffering from malnutrition 2018        | Potensi desa BPS 2019                                   | number         |
| 44  | Annual mean temperature                                 | WORLDCLIM 2.1                                           | 0 C            |
| 45  | Temperature changes                                     | WORLDCLIM 2.1                                           | 0 C            |
| 46  | Annual mean precipitation                               | WORLDCLIM 2.1                                           | mm             |
| 47  | Precipitation changes                                   | WORLDCLIM 2.1                                           | mm             |
| 48  | rasio_40pers_ekon_rendah_RT                             | National Team for the Acceleration of Poverty Reduction | number         |
| 49  | rasio_40pers_ekon_rendah_Indv                           | National Team for the Acceleration of Poverty Reduction | number         |
| 50  | Distance to irrigated land                              | Ministry of Public Works and Housing                    | m              |
| 51  | Percentage of irrigated land                            | Ministry of Public Works and Housing                    | ha             |
| 52  | Wet months                                              | WORLDCLIM 2.1                                           | months         |

@@

|-----------------|-----------------|-----------------|---------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|-----------------|-----------------|-----------------|---------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |

>>>>

### List of collected features
| No  | Feature                                                    | Source                                                  | Unit           |
|---------------|-------------------------|------------------|---------------|

@@

| 14  | Deforestation area size                                 | Land cover map 2020, MoEF                               | km^2^            |
| 15  | Arable land                                         | Land cover map 2020, MoEF                               | % |
| 16  | Erosion                                                 | RUSLE                                                   | t ha^-1^ yr^-1^    |

@@

| 20  | Number of Households | Potensi desa BPS 2019                                   | number         |
| 21  | Electrification ratio                                   | Potensi desa BPS 2019                                   | \%         |
| 22  | High school                                        | Potensi desa BPS 2019                                   | number         |
| 23  | University                                         | Potensi desa BPS 2019                                   | number         |
| 24  | Hospital                                           | Potensi desa BPS 2019                                   | number         |
| 25  | Health facility                                    | Potensi desa BPS 2019                                   | number         |
| 26  | Market                                             | Potensi desa BPS 2019                                   | number         |
| 27  | Minimarket                                         | Potensi desa BPS 2019                                   | number         |

@@

| 40  | Reservoir                                          | Potensi desa BPS 2019                                   | number         |
| 41  | Village markets                                | Potensi desa BPS 2019                                   | number         |
| 42  | Number of people suffering from malnutrition 2018       | Potensi desa BPS 2019                                   | individuals         |
| 43  | Annual mean temperature                                 | WORLDCLIM 2.1                                           | °C            |
| 44  | Temperature changes                                     | WORLDCLIM 2.1 & MRI-ESM2-0 SSP 245 2050s                                          | °C            |
| 45  | Annual mean precipitation                               | WORLDCLIM 2.1                                          | mm             |
| 46  | Precipitation changes                                   | WORLDCLIM 2.1 & MRI-ESM2-0 SSP 245 2050s                                        | mm             |
| 47  | Households in the lowest 40% of the economic bracket                             | National Team for the Acceleration of Poverty Reduction | \%         |
| 48  | Distance to irrigated land                              | Ministry of Public Works and Housing                    | m              |
| 49  | Percentage of irrigated land                            | Ministry of Public Works and Housing                    | \%             |
| 50  | Wet months                                              | WORLDCLIM 2.1                                           | months         |

### A sample of ready-to-process data

@@

|------------------|------------------|------------------|--------------------|

@@

| **Typology** | **R.3.1 Establishment of Peatland Stewardship Village**                                                                                                                                                                                                               | **R.3.2 Enhancing Livelihood Capacity**                                                                                                          | **R.3.3 Development of Alternative Commodities and Livelihood Sources**                                                             |
|------------------|------------------|------------------|--------------------|
| **1**        | \- Community awareness about the importance of the peat ecosystem, collaborating with district and provincial governments. <br><br> - Activities of the Peatland Stewardship Village aimed at increasing income and creating sources of livelihood for the community. | Conducted in synergy with district/city governments.                                                                                             | Directed at non-agricultural livelihood sources (off-farm). Local industries that exist need support.                               |
| **2**        | Peatland Stewardship Village is executed in an integrated manner in partnership with HTI companies and palm oil plantations. The goal is to enhance community access.                                                                                                 | Strengthening farmers' livelihoods to protect the remaining peat ecosystems. Formulation of alternative livelihood sources.                      | Livelihood sources oriented towards peat-friendly agriculture, mixed plantations combined with non-agricultural livelihood sources. |
| **3**        | Peatland Stewardship Village is oriented towards fire prevention; conducted in an integrated manner in partnership with HTI companies and palm oil plantations.                                                                                                       | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Livelihoods aimed at forest and land fire prevention. | Livelihood sources oriented towards peat-friendly agriculture and plantations combined with fisheries and livestock.                |
| **4**        | Peatland Stewardship Village geared towards fire prevention; enhancing community access to markets and high-economic value commodities.                                                                                                                               | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
| **5**        | Peatland Stewardship Village focused on fire prevention; enhancing community access to markets and commodities of high economic value.                                                                                                                                | Strengthening farmers' livelihoods through partnerships with plantation and HTI companies. Emphasis on preventing forest and land fires.         | Livelihood sources focused on peat-friendly agriculture and plantations combined with fisheries and livestock.                      |
